Final Report: Measles risk assessment, modelling, and benefit--cost analyses for New Zealand

### 2015-07-17 draftfinalreport_v4.Rnw
fixup vaccine break-even point to generate from true value

Our estimates for the benefit--cost ratio of catch up immunisation are similar to those in other countries. Estimates in Korea suggest catch up immunisation schemes have a benefit--cost ratio of just over one \citep{bae13}. If we presume the $R_0$ estimated for measles in New Zealand is representative and following \Sexpr{vacc_reqd_percent}\% immunisation of the na\"{\i}ve population, measles will be unable to persist ($R_v$ < 1), our B/C ratio is greater than 1. At the national level our B/C ratio is > 1 for either \$50 or \$20 effective immunisation costs. However, the B/C ratios do vary substantially by DHB, with those with smaller populations least cost effective for immunisation programmes. However, the estimated B/C ratio for MMR has been estimated to be between 10.2 and 54.2, much greater than one (see \autoref{table:zhou2}) \citep{zhou4}. As stated above, these authors also consider the costs and benefits of mumps and rubella, so making direct comparison difficult without reanalysis. Our results are relatively insensitive to changes in immunisation cost, requiring high costs (>\$1,117 per immunised person at the national level) before immunisation is predicted to not be beneficial. Similarly, longer discounting periods or 5\% discounting did not affect reduce the B/C ratio substantially (not shown). A spreadsheet is provided for the Ministry to work with.

>>>>

Our estimates for the benefit--cost ratio of catch up immunisation are similar to those in other countries. Estimates in Korea suggest catch up immunisation schemes have a benefit--cost ratio of just over one \citep{bae13}. If we presume the $R_0$ estimated for measles in New Zealand is representative and following \Sexpr{vacc_reqd_percent}\% immunisation of the na\"{\i}ve population, measles will be unable to persist ($R_v$ < 1), our B/C ratio is greater than 1. At the national level our B/C ratio is > 1 for either \$50 or \$20 effective immunisation costs. However, the B/C ratios do vary substantially by DHB, with those with smaller populations least cost effective for immunisation programmes. However, the estimated B/C ratio for MMR has been estimated to be between 10.2 and 54.2, much greater than one (see \autoref{table:zhou2}) \citep{zhou4}. As stated above, these authors also consider the costs and benefits of mumps and rubella, so making direct comparison difficult without reanalysis. Our results are relatively insensitive to changes in immunisation cost, requiring high costs (>\$\Sexpr{break_even_vacc_cost} per immunised person at the national level) before immunisation is predicted to not be beneficial. Similarly, longer discounting periods or 5\% discounting did not affect the B/C ratio substantially (not shown). A spreadsheet is provided for the Ministry to work with.
